\documentclass[aspectratio=1610]{beamer}
% This can be compiled with pdflatex.
% Load fontspec so that you can load OTF/TTF fonts if you want to; but then you must compile with xelatex or lualatex!
% \usepackage{fontspec} 

% beamerthemeMirage.sty v1.0 2024/04/14
% by LianTze Lim (liantze@gmail.com)
% A beamer theme inspired by Zhou Shen's `Mirage' song poster
% \usetheme{Mirage}           % Default = dark mode
\usetheme[light]{Mirage}  % Alternative light mode 

% The glowy light in the footnline
% \setlength{\MirageGlowRadius}{0.25ex}

% Mirage theme loads the fontawesome5 package

\title{Mirage Theme}
\subtitle{Inspired by the song poster of the lead single, \emph{Mirage}}
\author{LianTze Lim}
\institute{The full album \emph{Shenself} now available on all major music  platforms}
\date{2024/10/22}

\usepackage{iftex}

% These fonts will work with pdflatex, xelatex, lualatex
\usepackage[lining,tabular]{carlito}
\usepackage{caladea}

\ifboolexpr{bool{xetex} or bool{luatex}}{
  % Unicode-math and TTF/OTF fonts will only work with xelatex, lualatex
  \usepackage{unicode-math}
  % \setmathfont{STIX Two Math}
  % \setmathfont{Erewhon Math}
  \setmathfont{Fira Math}
}{% Sans math font in pdflatex:
  \usepackage[T1]{fontenc}
  \usepackage{newtxsf}
}


\begin{document}

\frame{\maketitle}

\section{Intro}
\begin{frame}
\frametitle{Introduction}

\begin{itemize}
    \item Behold the mechanical dove \faDove{} flying through the air 
    \item How might its eyes be lit \faEye[regular] that it appears lifelike

\begin{enumerate}
    \item Are digital dawns and dusks \faCloudSun{} more colourful? \faCloudMoon
    \item Are bionic lovers \faGrinHearts{} more loyal? \faGrin*[regular]
\end{enumerate}

    \item Push this one door open \faDoorOpen{} and there are thousands more \faDoorClosed{\small\faDoorClosed}{\footnotesize\faDoorClosed}{\scriptsize\faDoorClosed}{\tiny\faDoorClosed}
\end{itemize}

\end{frame}

\subsection{Lists}
\begin{frame}
\frametitle{The ancient gaze from aeons ago}
    \begin{enumerate}
        \item How might it discern if this moment is fantasy or real
        \begin{enumerate}
	        \item Is man-made talent true inherent wisdom?
	        \begin{enumerate}
		        \item Do cloned bodies have souls?
		        \item Forever questioning, but ever without a conclusion
	        \end{enumerate}
        \end{enumerate}
        \item \alert{Can it be real}
    \end{enumerate}

\end{frame}

\section{Blocks}

\begin{frame}[c]
\frametitle{The Heavenward Staircase of Wisdom is ever endless}
\begin{columns}
\begin{column}[b]{.35\textwidth}
\begin{pullquote}
    Can it be real\\
    The world is a mirage
\end{pullquote}
\end{column}

\begin{column}[t]{.65\textwidth}
\setbeamercolor{pullquote}{fg=MirageBlue}
\renewcommand{\MiragePullquoteOpen}{«}
\begin{pullquote}
Amidst barren hills of electronic fantasies\\
I search for oases of truth\\
Though as small as mayflies\\
I dare gaze at the galaxies
\end{pullquote}
\end{column}
\end{columns}
\end{frame}


% \renewcommand{\MirageFrametitlePrefix}{\faDove}
% \renewcommand{\MirageProofPrefix}{\faCheckSquare[regular]}
% \renewcommand{\MirageTheoremPrefix}{\faCogs}

\begin{frame}[allowframebreaks]{Blocks blocks blocks 123}

    \begin{exampleblock}{Gosh I've no idea what I'm writing, do you?}
    Now solve $x = \frac{-b \pm \sqrt{b^2 -4ac}}{2a}$. This should be easy, right?
    \end{exampleblock}

    \begin{alertblock}{Gosh I've no idea what I'm writing, do you?}
    \[ x = \frac{-b \pm \sqrt{b^2 -4ac}}{2a}, \quad\therefore \alpha \neq \Omega \]
    \end{alertblock}

    \begin{block}{Gosh I've no idea what I'm writing, do you?}
    \[ x = \frac{-b \pm \sqrt{b^2 -4ac}}{2a}, \quad\therefore \alpha \neq \Omega \]
    \end{block}
    
    \begin{proof}
    As everyone can clearly see, $1+1=2$.
    \end{proof}

    \begin{theorem}
    A wonderful thing is about to happen -- it \emph{will} eventually happen.
    \end{theorem}
    
    \begin{definition}
    A wonderful thing is about to happen -- it \emph{will} eventually happen.
    \end{definition}
\end{frame}


\end{document}
